\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2018-10-15 paper/sp.tex
get rid of interpretation parts

The linear model we use has a big limitation: Linear models are inflexible.
However, it has a great advantage over more general methods,
which is that it is easy to look inside
the linear model and check whether the dependencies represented there make sense.
The feature vector $x_n$ for star $n$
contains a set of photometry in magnitudes.
Linear combinations of these photometric measurements are like complex synthetic
magnitudes or colors.
Since the model was trained to deliver luminosities of stars given training data
of different metallicities and extinctions, the synthetic photometry developed
by the model should be, in some sense, metallicity- and extinction-independent
photometry for luminous red-giant stars!
In detail this synthetic magnitude is something like HOGG PUT EQUATION HERE AND
SAY SOMETHING ABOUT IT. HOGG: Maybe plot this synthetic photometry against dust
and metallicity.

HOGG: Similarly, the spectral part of the model should also be
interpretable. HOGG DESCRIBE \figurename~\ref{fig:spectral} THAT
DEMONSTRATES THIS, qualitatively.
\begin{figure}
\includegraphics[width=\textwidth]{coefficients.pdf}
\caption{HOGG: THIS FIGURE ISN'T READY YET:
  The coefficients of the spectral part of the linear model.
  Also shown are derivatives with respect to labels for a \project{Cannon}-like
  linear regression for the Training Set data.\label{fig:spectral}}
\end{figure}

@@

>>>>

@@

Another  advantage of a linear model over more general methods (like deep learning, say),
is that it is possible to look inside
the linear model and check whether the dependencies represented there make sense.
For example, the feature vector $x_n$ for star $n$
contains a set of photometry in magnitudes.
Linear combinations of these photometric measurements are like complex synthetic
magnitudes or colors.
Similarly, linear combinations of spectral pixels are like a projection of the spectral space.
Brief inspection of these linear combinations showed them to be sensible, but it is out of
scope here to interpret them in detail.
